---
title: "LDP Project T3"
author: "Chloe Hunt and Amina Harrath"
format: revealjs
editor: visual
---

## Trauma and memory

We're examining factors that predict hot memory encoding of traumatic events in children. The project is grounded in the premise that traumatic experiences activate a psychological alarm response, leading to heightened amygdala activity and suppressed hippocampal function.

This neurological profile contributes to non-optimal encoding, in which emotional, cognitive, sensory and physiological aspects of the event (hot memories) are stored without their temporal and spatial context (cold memory). Such disturbances may underpin subjective experiences like flashbacks.

Interventions such as Narrative Exposure Therapy (NET) place traumatic events in chronological order as way to re-process the memories through a slow and detailed reliving connecting the hot and cold memory together with additional awareness and recognition of the wider context and meaning of these events for the individual.

## Data set

We are using the UK Data Service PROTECT data set that captures measures exploring the role of trauma specific behaviours and parenting style in facilitating child psychological adjustment.

The data set includes self-reported questionnaires of children and parents who have experienced a traumatic event, including:

-   Child Post-trauma Behaviour Questionnaire

-   Child Post-trauma Cognition Inventory Questionnaire

-   Parent Trauma Response Questionnaire

## Data set

The collection contains data from three time points:

-   T1: Within six weeks of the traumatic event

-   T2: Three months after the traumatic event

-   T3: Six months after the traumatic event

```{r}
#| label: ‘Set up’
#| echo: false

# Load libraries
library(haven)
library(dplyr)
library(ggplot2)
library(tidyr)
library(lavaan)
library(gridExtra)

## Load data
## Parental questionnaires 
# Parental Trauma Responses Questionnaire 
PQRST_t1 <- read_sav("00.Raw_Data/T1/Parent/p1_PTRQ_(Parent Trauma Response Questionnaire).sav")
PQRST_t2 <- read_sav("00.Raw_Data/T2/Parent/p2_PTRQ_(Parent Trauma Response Questionnaire).sav")
PQRST_t3 <- read_sav("00.Raw_Data/T3/Parent/p3_PTRQ_(Parent Trauma Response Questionnaire).sav")

# Parental overprotection scale
POI_t1 <- read_sav("00.Raw_Data/T1/Parent/p1_POI_(Parental Overprotection Scale.sav")
POI_t2 <- read_sav("00.Raw_Data/T2/Parent/p2_POI_(Parental Overprotection Scale).sav")
POI_t3 <- read_sav("00.Raw_Data/T3/Parent/p3_POI_(Parental Overprotection Scale).sav")

# Child questionnaires
# Child Post-Traumatic Cognition Inventory
CPTCI_t1 <- read_sav("00.Raw_Data/T1/Child and Teenager/c1_CPTCI_(Child Posttraumatic Cognitions Inventory).sav")
CPTCI_t2 <- read_sav("00.Raw_Data/T2/Child and Teenager/c2_CPTCI_(Child Postraumatic Cognitions Inventory).sav")
CPTCI_t3 <- read_sav("00.Raw_Data/T3/Child and Teenager/c3_CPTCI_(Child Posttraumatic Cognitions Inventory).sav")

# Multidimensional scale of perceived social support
MPSS_t1 <- read_sav("00.Raw_Data/T1/Child and Teenager/c1_MSPSS (Multidimensional Scale of Perceived Social Support).sav")
MPSS_t2 <- read_sav("00.Raw_Data/T2/Child and Teenager/c2_MSPSS (Multidimensional Scale of Perceived Social Support).sav")

# Child posttrauma behaviour questionnaire
CPBQ_t1 <- read_sav("00.Raw_Data/T1/Child and Teenager/c1_CPBQ_(Child Posttrauma Behaviours Questionnaire).sav")
CPBQ_t2 <- read_sav("00.Raw_Data/T2/Child and Teenager/c2_CPBQ_(Child Posttrauma Behaviours Questionnaire).sav")
CPBQ_t3 <- read_sav("00.Raw_Data/T3/Child and Teenager/c3_CPBQ_(Child Posttrauma Behaviours Questionnaire).sav")

# Child memory questionnaire
ACTMQ_t1 <- read_sav("00.Raw_Data/T1/Child and Teenager/c1_ACTMQ_(Adapted Child Trauma Memory Questionnaire).sav")
ACTMQ_t2 <- read_sav("00.Raw_Data/T2/Child and Teenager/c2_ACTMQ_(Adapted Child Trauma Memory Questionnaire).sav")
ACTMQ_t3 <- read_sav("00.Raw_Data/T3/Child and Teenager/c3_ACTMQ_(Adapted Child Trauma Memory Questionnaire).sav")


## Merge the dataset wide

# Merge parent datasets
# Standardize IDs to 3-digit character format with leading zeros
PQRST_t1 <- PQRST_t1 |>
  mutate(ID = sprintf("%03d", as.integer(ID)))
POI_t1 <- POI_t1 |>
  mutate(ID = as.character(ID))  # Just to be safe
parent_t1 <- PQRST_t1 |>
  full_join(POI_t1, by = "ID", suffix = c("_pqrst", "_poi"))

# Time 2
PQRST_t2 <- PQRST_t2 |>
  mutate(ID = sprintf("%03d", as.integer(ID)))
POI_t2 <- POI_t2 |>
  mutate(ID = as.character(ID))  # Just to be safe
parent_t2 <- PQRST_t2 |>
  full_join(POI_t2, by = "ID", suffix = c("_pqrst", "_poi"))

# Time 3
PQRST_t3 <- PQRST_t3 |>
  mutate(ID = sprintf("%03d", as.integer(ID)))
POI_t3 <- POI_t3 |>
  mutate(ID = as.character(ID))  # Just to be safe
parent_t3 <- PQRST_t3 |>
  full_join(POI_t3, by = "ID", suffix = c("_pqrst", "_poi"))

## Combine parent datasets wide
parent_t1 <- parent_t1 |> rename_with(~ paste0(.x, "_t1"), -ID)
parent_t2 <- parent_t2 |> rename_with(~ paste0(.x, "_t2"), -ID)
parent_t3 <- parent_t3 |> rename_with(~ paste0(.x, "_t3"), -ID)
parent_all <- parent_t1 |>
  full_join(parent_t2, by = "ID") |>
  full_join(parent_t3, by = "ID")
parent_all <- parent_all %>%
  mutate(dyad_ID = gsub("P_", "", ID))


## Merge child datasets wide
# Time 1
child_t1 <- CPBQ_t1 |>
  full_join(CPTCI_t1, by = "ID", suffix = c("_cpbq", "_cptci")) |>
  full_join(ACTMQ_t1, by = "ID", suffix = c("", "_actmq"))

# Time 2
child_t2 <- CPBQ_t2 |>
  full_join(CPTCI_t2, by = "ID", suffix = c("_cpbq", "_cptci")) |>
  full_join(ACTMQ_t2, by = "ID", suffix = c("", "_actmq"))

# Time 3
child_t3 <- CPBQ_t3 |>
  full_join(CPTCI_t3, by = "ID", suffix = c("_cpbq", "_cptci")) |>
  full_join(ACTMQ_t3, by = "ID", suffix = c("", "_actmq"))

## Combine child datasets wide
child_t1 <- child_t1 |> rename_with(~ paste0(.x, "_t1"), -ID)
child_t2 <- child_t2 |> rename_with(~ paste0(.x, "_t2"), -ID)
child_t3 <- child_t3 |> rename_with(~ paste0(.x, "_t3"), -ID)
child_all <- child_t1 |>
  full_join(child_t2, by = "ID") |>
  full_join(child_t3, by = "ID")

child_all <- child_all %>%
  mutate(dyad_ID = gsub("C_", "", ID))


## 
# Remove prefixes and create a common dyad ID
dyad_all <- full_join(child_all, parent_all, by = "dyad_ID", suffix = c("_child", "_parent"))
dyad_all <- dyad_all %>%
  relocate(dyad_ID, ID_child, ID_parent, .before = everything())

dyad_all_clean <- dyad_all %>%
  select(dyad_ID,
         matches("actmq_q(3|5|7|12|15|17)"),
                 matches("cpbq_a_q(1|2|3|5)"),
                  matches("cpbq_b_q(1|2|9|10|11)"),
         matches("cptci_q(6|14|19|23|24|1|5|10|18|25)"),
      matches("pqrst_bq(3|4|5|10|11|15|20|22|23|24|26|34)"),
      matches("pqrst_aq(2|4|6|9|14|17|22|26|27|29|31|33|34|35|36|37|41|42)"))
      
```

## Hypotheses

1.  **H1:** Higher levels of maladaptive child beliefs will be associated with greater hot memory encoding of the traumatic event

2.  **H2:** Higher levels of child maladaptive behaviours will be associated with greater hot memory encoding

3.  **H3:** Child beliefs will indirectly influence hot memory encoding through their impact on child behaviours

4.  **H4:** Parental trauma-related beliefs will be associated with more maladaptive child beliefs

5.  **H5:** Parental trauma-related beliefs will influence child beliefs indirectly through their effect on parental behaviours

## Parenting behaviour in response to trauma over time

```{r}
#| label: ‘Parent behaviour data visualisation set up’
#| echo: false
#| output: false
glimpse(parent_all)
summary(parent_all)

# T1: PARENT BEHAVIOURS
PQRST_t1_freq <- lapply(PQRST_t1[ , !(names(PQRST_t1) %in% c("ID", "Date")) ], table)
PQRST_t1_freq

# overprotectiveness
PQRST_t1_op_freq <- PQRST_t1_freq[c("p1_pqrst_bq34", "p1_pqrst_bq27", "p1_pqrst_bq2", "p1_pqrst_bq10", "p1_pqrst_bq18", "p1_pqrst_bq5")]
PQRST_t1_op_freq <- Reduce(`+`, PQRST_t1_op_freq)
print(PQRST_t1_op_freq)

# discussions with child regarding danger/safety
PQRST_t1_dsd_freq <- PQRST_t1_freq[c("p1_pqrst_bq12", "p1_pqrst_bq30", "p1_pqrst_bq22", "p1_pqrst_bq28", "p1_pqrst_bq33")]
PQRST_t1_dsd_freq <- Reduce(`+`, PQRST_t1_dsd_freq)
print(PQRST_t1_dsd_freq)

# avoidance of discussion
PQRST_t1_aod_freq <- PQRST_t1_freq[c("p1_pqrst_bq24", "p1_pqrst_bq1", "p1_pqrst_bq24", "p1_pqrst_bq4", "p1_pqrst_bq3", "p1_pqrst_bq29", "p1_pqrst_bq14", "p1_pqrst_bq15", "p1_pqrst_bq23", "p1_pqrst_bq17", "p1_pqrst_bq11", "p1_pqrst_bq7", "p1_pqrst_bq32", "p1_pqrst_bq13")]

reverse_items <- c("p1_pqrst_bq23", "p1_pqrst_bq17", "p1_pqrst_bq11",
                   "p1_pqrst_bq7", "p1_pqrst_bq32", "p1_pqrst_bq13")
PQRST_t1_aod_freq[reverse_items] <- lapply(PQRST_t1_aod_freq[reverse_items], \(x) {
  names(x) <- as.character(3 - as.numeric(names(x))); x[order(as.numeric(names(x)))]
})

PQRST_t1_aod_freq <- Reduce(`+`, PQRST_t1_aod_freq)
print(PQRST_t1_aod_freq)


# avoiding reminders
PQRST_t1_ar_freq <- PQRST_t1_freq[c("p1_pqrst_bq9", "p1_pqrst_bq6", "p1_pqrst_bq8", "p1_pqrst_bq31", "p1_pqrst_bq25", "p1_pqrst_bq20", "p1_pqrst_bq16", "p1_pqrst_bq19", "p1_pqrst_bq26")]

reverse_items2 <- c("p1_pqrst_bq25", "p1_pqrst_bq20", "p1_pqrst_bq16",
                   "p1_pqrst_bq19", "p1_pqrst_bq26")
PQRST_t1_ar_freq[reverse_items] <- lapply(PQRST_t1_ar_freq[reverse_items2], \(x) {
  names(x) <- as.character(3 - as.numeric(names(x))); x[order(as.numeric(names(x)))]
})

PQRST_t1_ar_freq <- Reduce(`+`, PQRST_t1_ar_freq)
print(PQRST_t1_ar_freq)


# Converts a named frequency table to proportions
to_proportions <- function(freq_table) {
  prop_table <- freq_table / sum(freq_table)
  return(prop_table)
  }

PQRST_t1_op_prop  <- to_proportions(PQRST_t1_op_freq)
PQRST_t1_dsd_prop <- to_proportions(PQRST_t1_dsd_freq)
PQRST_t1_aod_prop <- to_proportions(PQRST_t1_aod_freq)
PQRST_t1_ar_prop  <- to_proportions(PQRST_t1_ar_freq)

prop_to_df <- function(prop_table, group_name) {
  df <- as.data.frame(prop_table)
  colnames(df) <- c("FreqPoint", "Proportion")
  df$FreqPoint <- factor(df$FreqPoint, levels = c("0","1","2","3"))
  df$Group <- group_name
  return(df)
}

# Create data frames from each proportion table
df_t1_op_prop  <- prop_to_df(PQRST_t1_op_prop,  "op")
df_t1_dsd_prop <- prop_to_df(PQRST_t1_dsd_prop, "dsd")
df_t1_aod_prop <- prop_to_df(PQRST_t1_aod_prop, "aod")
df_t1_ar_prop  <- prop_to_df(PQRST_t1_ar_prop,  "ar")

# Combine
df_t1_prop <- bind_rows(df_t1_op_prop, df_t1_dsd_prop, df_t1_aod_prop, df_t1_ar_prop)

## PARENT BEHAVIOUR - T2
PQRST_t2_freq <- lapply(PQRST_t2[ , !(names(PQRST_t2) %in% c("ID", "Date")) ], table)
PQRST_t2_freq

# overprotectiveness
PQRST_t2_op_freq <- PQRST_t2_freq[c("p2_pqrst_bq34", "p2_pqrst_bq27", "p2_pqrst_bq2", "p2_pqrst_bq10", "p2_pqrst_bq18", "p2_pqrst_bq5")]
PQRST_t2_op_freq <- Reduce(`+`, PQRST_t2_op_freq)
print(PQRST_t2_op_freq)

# discussions with child regarding danger/safety
PQRST_t2_dsd_freq <- PQRST_t2_freq[c("p2_pqrst_bq12", "p2_pqrst_bq30", "p2_pqrst_bq22", "p2_pqrst_bq28", "p2_pqrst_bq33")]
PQRST_t2_dsd_freq <- Reduce(`+`, PQRST_t2_dsd_freq)
print(PQRST_t2_dsd_freq)

# avoidance of discussion
PQRST_t2_aod_freq <- PQRST_t2_freq[c("p2_pqrst_bq24", "p2_pqrst_bq1", "p2_pqrst_bq21", "p2_pqrst_bq4", "p2_pqrst_bq3", "p2_pqrst_bq29", "p2_pqrst_bq14", "p2_pqrst_bq15", "p2_pqrst_bq23", "p2_pqrst_bq17", "p2_pqrst_bq11", "p2_pqrst_bq7", "p2_pqrst_bq32", "p2_pqrst_bq13")]

reverse_items <- c("p2_pqrst_bq23", "p2_pqrst_bq17", "p2_pqrst_bq11",
                   "p2_pqrst_bq7", "p2_pqrst_bq32", "p2_pqrst_bq13")
PQRST_t2_aod_freq[reverse_items] <- lapply(PQRST_t2_aod_freq[reverse_items], \(x) {
  names(x) <- as.character(3 - as.numeric(names(x))); x[order(as.numeric(names(x)))]
})

expected_levels <- as.character(0:3)
PQRST_t2_aod_freq <- lapply(PQRST_t2_aod_freq, function(tbl) {
  tbl_full <- setNames(rep(0, length(expected_levels)), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)
})

PQRST_t2_aod_freq <- Reduce(`+`, PQRST_t2_aod_freq)
print(PQRST_t2_aod_freq)

# avoiding reminders
PQRST_t2_ar_freq <- PQRST_t2_freq[c("p2_pqrst_bq9", "p2_pqrst_bq6", "p2_pqrst_bq8", "p2_pqrst_bq31", "p2_pqrst_bq25", "p2_pqrst_bq20", "p2_pqrst_bq16", "p2_pqrst_bq19", "p2_pqrst_bq26")]

reverse_items2 <- c("p2_pqrst_bq25", "p2_pqrst_bq20", "p2_pqrst_bq16",
                   "p2_pqrst_bq19", "p2_pqrst_bq26")
PQRST_t2_ar_freq[reverse_items] <- lapply(PQRST_t2_ar_freq[reverse_items2], \(x) {
  names(x) <- as.character(3 - as.numeric(names(x))); x[order(as.numeric(names(x)))]
})


PQRST_t2_ar_freq <- lapply(PQRST_t2_ar_freq, function(tbl) {
  tbl_full <- setNames(rep(0, length(expected_levels)), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)
})

PQRST_t2_ar_freq <- Reduce(`+`, PQRST_t2_ar_freq)
print(PQRST_t2_ar_freq)

## converting to proportions
PQRST_t2_op_prop  <- to_proportions(PQRST_t2_op_freq)
PQRST_t2_dsd_prop <- to_proportions(PQRST_t2_dsd_freq)
PQRST_t2_aod_prop <- to_proportions(PQRST_t2_aod_freq)
PQRST_t2_ar_prop  <- to_proportions(PQRST_t2_ar_freq)

prop_to_df <- function(x, group_name) {
  expected_levels <- as.character(0:3)
  
  # Pad missing levels with 0
  padded <- setNames(rep(0, length(expected_levels)), expected_levels)
  padded[names(x)] <- x
  
  data.frame(
    Group = group_name,
    FreqPoint = factor(names(padded), levels = expected_levels,
                       labels = c("Not at all", "A little", "Some", "A lot")),
    Proportion = as.numeric(padded))} 

df_t2_op_prop  <- prop_to_df(PQRST_t2_op_prop,  "op")
df_t2_dsd_prop <- prop_to_df(PQRST_t2_dsd_prop, "dsd")
df_t2_aod_prop <- prop_to_df(PQRST_t2_aod_prop, "aod")
df_t2_ar_prop  <- prop_to_df(PQRST_t2_ar_prop,  "ar")

df_t2_prop <- bind_rows(df_t2_op_prop, df_t2_dsd_prop, df_t2_aod_prop, df_t2_ar_prop)


### PARENT BEHAVIOUR - T3
PQRST_t3_freq <- lapply(PQRST_t3[ , !(names(PQRST_t3) %in% c("ID", "Date")) ], table)
PQRST_t3_freq

# overprotectiveness
PQRST_t3_op_freq <- PQRST_t3_freq[c("p3_pqrst_bq34", "p3_pqrst_bq27", "p3_pqrst_bq2", "p3_pqrst_bq10", "p3_pqrst_bq18", "p3_pqrst_bq5")]

PQRST_t3_op_freq <- lapply(PQRST_t3_op_freq, function(tbl) {
  names(tbl) <- as.character(names(tbl))  # ensure names are characters
  if ("4" %in% names(tbl)) {
    # Add the count at '4' to '3', or create '3' if missing
    tbl["3"] <- sum(tbl["3"], tbl["4"], na.rm = TRUE)
    tbl <- tbl[names(tbl) != "4"]  # remove the '4' entry
  }
  return(tbl)})

# Pad each frequency table with missing levels set to zero
PQRST_t3_op_freq <- lapply(PQRST_t3_op_freq, function(tbl) {
  full_tbl <- setNames(rep(0, length(expected_levels)), expected_levels)
  full_tbl[names(tbl)] <- tbl
  return(full_tbl)})

PQRST_t3_op_freq <- Reduce(`+`, PQRST_t3_op_freq)
print(PQRST_t3_op_freq)

# discussions with child regarding danger/safety
PQRST_t3_dsd_freq <- PQRST_t3_freq[c("p3_pqrst_bq12", "p3_pqrst_bq30", "p3_pqrst_bq22", "p3_pqrst_bq28", "p3_pqrst_bq33")]
PQRST_t3_dsd_freq <- Reduce(`+`, PQRST_t3_dsd_freq)
print(PQRST_t3_dsd_freq)

# avoidance of discussion
PQRST_t3_aod_freq <- PQRST_t3_freq[c("p3_pqrst_bq24", "p3_pqrst_bq1", "p3_pqrst_bq21", "p3_pqrst_bq4", "p3_pqrst_bq3", "p3_pqrst_bq29", "p3_pqrst_bq14", "p3_pqrst_bq15", "p3_pqrst_bq23", "p3_pqrst_bq17", "p3_pqrst_bq11", "p3_pqrst_bq7", "p3_pqrst_bq32", "p3_pqrst_bq13")]

reverse_items <- c("p3_pqrst_bq23", "p3_pqrst_bq17", "p3_pqrst_bq11",
                   "p3_pqrst_bq7", "p3_pqrst_bq32", "p3_pqrst_bq13")
PQRST_t3_aod_freq[reverse_items] <- lapply(PQRST_t3_aod_freq[reverse_items], \(x) {
  names(x) <- as.character(3 - as.numeric(names(x))); x[order(as.numeric(names(x)))]
})

expected_levels <- as.character(0:3)
PQRST_t3_aod_freq <- lapply(PQRST_t3_aod_freq, function(tbl) {
  tbl_full <- setNames(rep(0, length(expected_levels)), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)
})

PQRST_t3_aod_freq <- Reduce(`+`, PQRST_t3_aod_freq)
print(PQRST_t3_aod_freq)

# avoiding reminders
PQRST_t3_ar_freq <- PQRST_t3_freq[c("p3_pqrst_bq9", "p3_pqrst_bq6", "p3_pqrst_bq8", "p3_pqrst_bq31", "p3_pqrst_bq25", "p3_pqrst_bq20", "p3_pqrst_bq16", "p3_pqrst_bq19", "p3_pqrst_bq26")]

reverse_items2 <- c("p3_pqrst_bq25", "p3_pqrst_bq20", "p3_pqrst_bq16",
                   "p3_pqrst_bq19", "p3_pqrst_bq26")
PQRST_t3_ar_freq[reverse_items] <- lapply(PQRST_t3_ar_freq[reverse_items2], \(x) {
  names(x) <- as.character(3 - as.numeric(names(x))); x[order(as.numeric(names(x)))]
})

PQRST_t3_ar_freq <- lapply(PQRST_t3_ar_freq, function(tbl) {
  tbl_full <- setNames(rep(0, length(expected_levels)), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)
})

PQRST_t3_ar_freq <- Reduce(`+`, PQRST_t3_ar_freq)
print(PQRST_t3_ar_freq)

## converting to proportions
PQRST_t3_op_prop  <- to_proportions(PQRST_t3_op_freq)
PQRST_t3_dsd_prop <- to_proportions(PQRST_t3_dsd_freq)
PQRST_t3_aod_prop <- to_proportions(PQRST_t3_aod_freq)
PQRST_t3_ar_prop  <- to_proportions(PQRST_t3_ar_freq)

prop_to_df <- function(x, group_name) {
  expected_levels <- as.character(0:3)
  
  # Pad missing levels with 0
  padded <- setNames(rep(0, length(expected_levels)), expected_levels)
  padded[names(x)] <- x
  
  data.frame(
    Group = group_name,
    FreqPoint = factor(names(padded), levels = expected_levels,
                       labels = c("Not at all", "A little", "Some", "A lot")),
    Proportion = as.numeric(padded))} 

df_t3_op_prop  <- prop_to_df(PQRST_t3_op_prop,  "op")
df_t3_dsd_prop <- prop_to_df(PQRST_t3_dsd_prop, "dsd")
df_t3_aod_prop <- prop_to_df(PQRST_t3_aod_prop, "aod")
df_t3_ar_prop  <- prop_to_df(PQRST_t3_ar_prop,  "ar")

df_t3_prop <- bind_rows(df_t3_op_prop, df_t3_dsd_prop, df_t3_aod_prop, df_t3_ar_prop)



```

```{r}
#| label: ‘Parent behaviour data visualisation’
#| echo: false
#| output: true

## Parent behaviour - t1
# Plot proportional stacked bar chart
p1_parent_behaviour <- ggplot(df_t1_prop, aes(x = Group, y = Proportion, fill = FreqPoint)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Parenting Behaviour",
    y = "Proportion",
    fill = "Response Level",
    title = "T1: within 6 weeks") +
  scale_x_discrete(
    labels = c(
      op = "Overprotectiveness",
      dsd = "Danger/Safety Conversations",
      aod = "Avoiding Trauma Discussion",
      ar = "Avoiding Reminders"
    )
  ) +
  scale_fill_manual(
    values = c("0" = "#d73027", "1" = "#fc8d59", "2" = "#fee090", "3" = "#91bfdb"),
    labels = c("0" = "Not at all", "1" = "A little", "2" = "Some", "3" = "A lot")) +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))

p2_parent_behaviour <- ggplot(df_t2_prop, aes(x = Group, y = Proportion, fill = FreqPoint)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Parenting Behaviour",
    y = "Proportion at T2",
    fill = "Response Level",
    title = "T2: after 3 months"
  ) + ylab(NULL) +
  scale_x_discrete(
    labels = c(
      op = "Overprotectiveness",
      dsd = "Danger/Safety Conversations",
      aod = "Avoiding Trauma Discussion",
      ar = "Avoiding Reminders"
    )
  ) +
  scale_fill_manual(
    values = c(
      "Not at all" = "#d73027",
      "A little"   = "#fc8d59",
      "Some"       = "#fee090",
      "A lot"      = "#91bfdb"
    )
  ) +
  theme_minimal() +
  theme(legend.position = "none",
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))


p3_parent_behaviour <- ggplot(df_t3_prop, aes(x = Group, y = Proportion, fill = FreqPoint)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Parenting Behaviour",
    y = "Proportion at T3",
    fill = "Response Level",
    title = "T3: after 6 months") +
  ylab(NULL) +
  scale_x_discrete(
    labels = c(
      op = "Overprotectiveness",
      dsd = "Danger/Safety Conversations",
      aod = "Avoiding Trauma Discussion",
      ar = "Avoiding Reminders")) +
  scale_fill_manual(
    values = c(
      "Not at all" = "#d73027",
      "A little"   = "#fc8d59",
      "Some"       = "#fee090",
      "A lot"      = "#91bfdb")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))

grid.arrange(p1_parent_behaviour, p2_parent_behaviour, p3_parent_behaviour, ncol = 3)


```

## Parenting beliefs in response to trauma over time

```{r}
#| label: ‘Parent beliefs data visualisation set up’
#| echo: false
#| output: false

### Parenting beliefs T1
# Permanent change/symptoms as threatening
PQRST_t1_pc_freq <- PQRST_t1_freq[c("p1_pqrst_aq27", "p1_pqrst_aq25", "p1_pqrst_aq8", "p1_pqrst_aq5", "p1_pqrst_aq12", "p1_pqrst_aq17", "p1_pqrst_aq9", "p1_pqrst_aq18")]

PQRST_t1_pc_freq <- lapply(PQRST_t1_pc_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_pc_freq <- Reduce(`+`, PQRST_t1_pc_freq)
print(PQRST_t1_pc_freq)

# family change and dynamic
PQRST_t1_fc_freq <- PQRST_t1_freq[c("p1_pqrst_aq1", "p1_pqrst_aq29", "p1_pqrst_aq10", "p1_pqrst_aq38", "p1_pqrst_aq28")]

PQRST_t1_fc_freq <- lapply(PQRST_t1_fc_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_fc_freq <- Reduce(`+`, PQRST_t1_fc_freq)
print(PQRST_t1_fc_freq)

# vulnerability and threat
PQRST_t1_vt_freq <- PQRST_t1_freq[c("p1_pqrst_aq23", "p1_pqrst_aq13", "p1_pqrst_aq19", "p1_pqrst_aq21", "p1_pqrst_aq39")]

PQRST_t1_vt_freq <- lapply(PQRST_t1_vt_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_vt_freq <- Reduce(`+`, PQRST_t1_vt_freq)
print(PQRST_t1_vt_freq)

# other people's reactions
PQRST_t1_opr_freq <- PQRST_t1_freq[c("p1_pqrst_aq44", "p1_pqrst_aq16", "p1_pqrst_aq34", "p1_pqrst_aq33", "p1_pqrst_aq4")]

PQRST_t1_opr_freq <- lapply(PQRST_t1_opr_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_opr_freq <- Reduce(`+`, PQRST_t1_opr_freq)
print(PQRST_t1_opr_freq)

# Inflated responsibility for ensuring safety
PQRST_t1_ir_freq <- PQRST_t1_freq[c("p1_pqrst_aq31", "p1_pqrst_aq2", "p1_pqrst_aq35", "p1_pqrst_aq30", "p1_pqrst_aq24")]

PQRST_t1_ir_freq <- lapply(PQRST_t1_ir_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_ir_freq <- Reduce(`+`, PQRST_t1_ir_freq)
print(PQRST_t1_ir_freq)

# rumination
PQRST_t1_r_freq <- PQRST_t1_freq[c("p1_pqrst_aq26", "p1_pqrst_aq14", "p1_pqrst_aq43", "p1_pqrst_aq42", "p1_pqrst_aq20", "p1_pqrst_aq3")]

PQRST_t1_r_freq <- lapply(PQRST_t1_r_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_r_freq <- Reduce(`+`, PQRST_t1_r_freq)
print(PQRST_t1_r_freq)

# self-blame
PQRST_t1_sb_freq <- PQRST_t1_freq[c("p1_pqrst_aq7", "p1_pqrst_aq32", "p1_pqrst_aq22", "p1_pqrst_aq11", "p1_pqrst_aq6")]

PQRST_t1_sb_freq <- lapply(PQRST_t1_sb_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_sb_freq <- Reduce(`+`, PQRST_t1_sb_freq)
print(PQRST_t1_sb_freq)

# parental tolerance and emotion
PQRST_t1_pte_freq <- PQRST_t1_freq[c("p1_pqrst_aq40", "p1_pqrst_aq15", "p1_pqrst_aq41", "p1_pqrst_aq36", "p1_pqrst_aq37")]

PQRST_t1_pte_freq <- lapply(PQRST_t1_pte_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t1_pte_freq <- Reduce(`+`, PQRST_t1_pte_freq)
print(PQRST_t1_pte_freq)

## converting to proportions
PQRST_t1_pc_prop  <- to_proportions(PQRST_t1_pc_freq)
PQRST_t1_fc_prop  <- to_proportions(PQRST_t1_fc_freq)
PQRST_t1_vt_prop  <- to_proportions(PQRST_t1_vt_freq)
PQRST_t1_opr_prop  <- to_proportions(PQRST_t1_opr_freq)
PQRST_t1_ir_prop  <- to_proportions(PQRST_t1_ir_freq)
PQRST_t1_r_prop  <- to_proportions(PQRST_t1_r_freq)
PQRST_t1_sb_prop  <- to_proportions(PQRST_t1_sb_freq)
PQRST_t1_pte_prop  <- to_proportions(PQRST_t1_pte_freq)

prop_to_df <- function(x, group_name) {
  expected_levels <- as.character(0:3)
  
  # Pad missing levels with 0
  padded <- setNames(rep(0, length(expected_levels)), expected_levels)
  padded[names(x)] <- x
  
  data.frame(
    Group = group_name,
    FreqPoint = factor(names(padded), levels = expected_levels,
                       labels = c("Not at all", "A little", "Some", "A lot")),
    Proportion = as.numeric(padded))} 

df_t1_pc_prop  <- prop_to_df(PQRST_t1_pc_prop,  "pc")
df_t1_fc_prop  <- prop_to_df(PQRST_t1_fc_prop,  "fc")
df_t1_vt_prop  <- prop_to_df(PQRST_t1_vt_prop,  "vt")
df_t1_opr_prop <- prop_to_df(PQRST_t1_opr_prop, "opr")
df_t1_ir_prop  <- prop_to_df(PQRST_t1_ir_prop,  "ir")
df_t1_r_prop   <- prop_to_df(PQRST_t1_r_prop,   "r")
df_t1_sb_prop  <- prop_to_df(PQRST_t1_sb_prop,  "sb")
df_t1_pte_prop <- prop_to_df(PQRST_t1_pte_prop, "pte")


df_t1_prop1 <- bind_rows(
  df_t1_pc_prop,
  df_t1_fc_prop,
  df_t1_vt_prop,
  df_t1_opr_prop,
  df_t1_ir_prop,
  df_t1_r_prop,
  df_t1_sb_prop,
  df_t1_pte_prop)

### Parenting beliefs T2
# Permanent change/symptoms as threatening
PQRST_t2_pc_freq <- PQRST_t2_freq[c("p2_pqrst_aq27", "p2_pqrst_aq25", "p2_pqrst_aq8", "p2_pqrst_aq5", "p2_pqrst_aq12", "p2_pqrst_aq17", "p2_pqrst_aq9", "p2_pqrst_aq18")]
 PQRST_t2_pc_freq <- lapply(PQRST_t2_pc_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_pc_freq <- Reduce(`+`, PQRST_t2_pc_freq)
print(PQRST_t2_pc_freq)
 
# family change and dynamic
PQRST_t2_fc_freq <- PQRST_t2_freq[c("p2_pqrst_aq1", "p2_pqrst_aq29", "p2_pqrst_aq10", "p2_pqrst_aq38", "p2_pqrst_aq28")]
 
PQRST_t2_fc_freq <- lapply(PQRST_t2_fc_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_fc_freq <- Reduce(`+`, PQRST_t2_fc_freq)
print(PQRST_t2_fc_freq)
 
# vulnerability and threat
PQRST_t2_vt_freq <- PQRST_t2_freq[c("p2_pqrst_aq23", "p2_pqrst_aq13", "p2_pqrst_aq19", "p2_pqrst_aq21", "p2_pqrst_aq39")]
 
PQRST_t2_vt_freq <- lapply(PQRST_t2_vt_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_vt_freq <- Reduce(`+`, PQRST_t2_vt_freq)
print(PQRST_t2_vt_freq)
 
# other people's reactions
PQRST_t2_opr_freq <- PQRST_t2_freq[c("p2_pqrst_aq44", "p2_pqrst_aq16", "p2_pqrst_aq34", "p2_pqrst_aq33", "p2_pqrst_aq4")]
 
PQRST_t2_opr_freq <- lapply(PQRST_t2_opr_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_opr_freq <- Reduce(`+`, PQRST_t2_opr_freq)
print(PQRST_t2_opr_freq)
 
# Inflated responsibility for ensuring safety
PQRST_t2_ir_freq <- PQRST_t2_freq[c("p2_pqrst_aq31", "p2_pqrst_aq2", "p2_pqrst_aq35", "p2_pqrst_aq30", "p2_pqrst_aq24")]
 
PQRST_t2_ir_freq <- lapply(PQRST_t2_ir_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_ir_freq <- Reduce(`+`, PQRST_t2_ir_freq)
print(PQRST_t2_ir_freq)
 
# rumination
PQRST_t2_r_freq <- PQRST_t2_freq[c("p2_pqrst_aq26", "p2_pqrst_aq14", "p2_pqrst_aq43", "p2_pqrst_aq42", "p2_pqrst_aq20", "p2_pqrst_aq3")]
 
PQRST_t2_r_freq <- lapply(PQRST_t2_r_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_r_freq <- Reduce(`+`, PQRST_t2_r_freq)
print(PQRST_t2_r_freq)
 
# self-blame
PQRST_t2_sb_freq <- PQRST_t2_freq[c("p2_pqrst_aq7", "p2_pqrst_aq32", "p2_pqrst_aq22", "p2_pqrst_aq11", "p2_pqrst_aq6")]
 
PQRST_t2_sb_freq <- lapply(PQRST_t2_sb_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_sb_freq <- Reduce(`+`, PQRST_t2_sb_freq)
print(PQRST_t2_sb_freq)
 
# parental tolerance and emotion
PQRST_t2_pte_freq <- PQRST_t2_freq[c("p2_pqrst_aq40", "p2_pqrst_aq15", "p2_pqrst_aq41", "p2_pqrst_aq36", "p2_pqrst_aq37")]
 
PQRST_t2_pte_freq <- lapply(PQRST_t2_pte_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
 
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})
 
PQRST_t2_pte_freq <- Reduce(`+`, PQRST_t2_pte_freq)
print(PQRST_t2_pte_freq)
 
## converting to proportions
PQRST_t2_pc_prop  <- to_proportions(PQRST_t2_pc_freq)
PQRST_t2_fc_prop  <- to_proportions(PQRST_t2_fc_freq)
PQRST_t2_vt_prop  <- to_proportions(PQRST_t2_vt_freq)
PQRST_t2_opr_prop  <- to_proportions(PQRST_t2_opr_freq)
PQRST_t2_ir_prop  <- to_proportions(PQRST_t2_ir_freq)
PQRST_t2_r_prop  <- to_proportions(PQRST_t2_r_freq)
PQRST_t2_sb_prop  <- to_proportions(PQRST_t2_sb_freq)
PQRST_t2_pte_prop  <- to_proportions(PQRST_t2_pte_freq)
 
prop_to_df <- function(x, group_name) {
  expected_levels <- as.character(0:3)
 
  # Pad missing levels with 0
  padded <- setNames(rep(0, length(expected_levels)), expected_levels)
  padded[names(x)] <- x
 
  data.frame(
	Group = group_name,
	FreqPoint = factor(names(padded), levels = expected_levels,
                       labels = c("Not at all", "A little", "Some", "A lot")),
	Proportion = as.numeric(padded))}
 
df_t2_pc_prop  <- prop_to_df(PQRST_t2_pc_prop,  "pc")
df_t2_fc_prop  <- prop_to_df(PQRST_t2_fc_prop,  "fc")
df_t2_vt_prop  <- prop_to_df(PQRST_t2_vt_prop,  "vt")
df_t2_opr_prop <- prop_to_df(PQRST_t2_opr_prop, "opr")
df_t2_ir_prop  <- prop_to_df(PQRST_t2_ir_prop,  "ir")
df_t2_r_prop   <- prop_to_df(PQRST_t2_r_prop,   "r")
df_t2_sb_prop  <- prop_to_df(PQRST_t2_sb_prop,  "sb")
df_t2_pte_prop <- prop_to_df(PQRST_t2_pte_prop, "pte")
 
 
df_t2_prop2 <- bind_rows(
  df_t2_pc_prop,
  df_t2_fc_prop,
  df_t2_vt_prop,
  df_t2_opr_prop,
  df_t2_ir_prop,
  df_t2_r_prop,
  df_t2_sb_prop,
  df_t2_pte_prop)


### Parent beliefs at T3
# Permanent change/symptoms as threatening
PQRST_t3_pc_freq <- PQRST_t3_freq[c("p3_pqrst_aq27", "p3_pqrst_aq25", "p3_pqrst_aq8", "p3_pqrst_aq5", "p3_pqrst_aq12", "p3_pqrst_aq17", "p3_pqrst_aq9", "p3_pqrst_aq18")]

PQRST_t3_pc_freq <- lapply(PQRST_t3_pc_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_pc_freq <- Reduce(`+`, PQRST_t3_pc_freq)
print(PQRST_t3_pc_freq)

# family change and dynamic
PQRST_t3_fc_freq <- PQRST_t3_freq[c("p3_pqrst_aq1", "p3_pqrst_aq29", "p3_pqrst_aq10", "p3_pqrst_aq38", "p3_pqrst_aq28")]

PQRST_t3_fc_freq <- lapply(PQRST_t3_fc_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_fc_freq <- Reduce(`+`, PQRST_t3_fc_freq)
print(PQRST_t3_fc_freq)

# vulnerability and threat
PQRST_t3_vt_freq <- PQRST_t3_freq[c("p3_pqrst_aq23", "p3_pqrst_aq13", "p3_pqrst_aq19", "p3_pqrst_aq21", "p3_pqrst_aq39")]

PQRST_t3_vt_freq <- lapply(PQRST_t3_vt_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_vt_freq <- Reduce(`+`, PQRST_t3_vt_freq)
print(PQRST_t3_vt_freq)

# other people's reactions
PQRST_t3_opr_freq <- PQRST_t3_freq[c("p3_pqrst_aq44", "p3_pqrst_aq16", "p3_pqrst_aq34", "p3_pqrst_aq33", "p3_pqrst_aq4")]

PQRST_t3_opr_freq <- lapply(PQRST_t3_opr_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_opr_freq <- Reduce(`+`, PQRST_t3_opr_freq)
print(PQRST_t3_opr_freq)

# Inflated responsibility for ensuring safety
PQRST_t3_ir_freq <- PQRST_t3_freq[c("p3_pqrst_aq31", "p3_pqrst_aq2", "p3_pqrst_aq35", "p3_pqrst_aq30", "p3_pqrst_aq24")]

PQRST_t3_ir_freq <- lapply(PQRST_t3_ir_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_ir_freq <- Reduce(`+`, PQRST_t3_ir_freq)
print(PQRST_t3_ir_freq)

# rumination
PQRST_t3_r_freq <- PQRST_t3_freq[c("p3_pqrst_aq26", "p3_pqrst_aq14", "p3_pqrst_aq43", "p3_pqrst_aq42", "p3_pqrst_aq20", "p3_pqrst_aq3")]

PQRST_t3_r_freq <- lapply(PQRST_t3_r_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_r_freq <- Reduce(`+`, PQRST_t3_r_freq)
print(PQRST_t3_r_freq)

# self-blame
PQRST_t3_sb_freq <- PQRST_t3_freq[c("p3_pqrst_aq7", "p3_pqrst_aq32", "p3_pqrst_aq22", "p3_pqrst_aq11", "p3_pqrst_aq6")]

PQRST_t3_sb_freq <- lapply(PQRST_t3_sb_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_sb_freq <- Reduce(`+`, PQRST_t3_sb_freq)
print(PQRST_t3_sb_freq)

# parental tolerance and emotion
PQRST_t3_pte_freq <- PQRST_t3_freq[c("p3_pqrst_aq40", "p3_pqrst_aq15", "p3_pqrst_aq41", "p3_pqrst_aq36", "p3_pqrst_aq37")]

PQRST_t3_pte_freq <- lapply(PQRST_t3_pte_freq, function(tbl) {
  if (is.null(tbl)) return(setNames(rep(0, 4), expected_levels))
  
  tbl_full <- setNames(rep(0, 4), expected_levels)
  tbl_full[names(tbl)] <- tbl
  return(tbl_full)})

PQRST_t3_pte_freq <- Reduce(`+`, PQRST_t3_pte_freq)
print(PQRST_t3_pte_freq)

## converting to proportions
PQRST_t3_pc_prop  <- to_proportions(PQRST_t3_pc_freq)
PQRST_t3_fc_prop  <- to_proportions(PQRST_t3_fc_freq)
PQRST_t3_vt_prop  <- to_proportions(PQRST_t3_vt_freq)
PQRST_t3_opr_prop  <- to_proportions(PQRST_t3_opr_freq)
PQRST_t3_ir_prop  <- to_proportions(PQRST_t3_ir_freq)
PQRST_t3_r_prop  <- to_proportions(PQRST_t3_r_freq)
PQRST_t3_sb_prop  <- to_proportions(PQRST_t3_sb_freq)
PQRST_t3_pte_prop  <- to_proportions(PQRST_t3_pte_freq)

prop_to_df <- function(x, group_name) {
  expected_levels <- as.character(0:3)
  
  # Pad missing levels with 0
  padded <- setNames(rep(0, length(expected_levels)), expected_levels)
  padded[names(x)] <- x
  
  data.frame(
    Group = group_name,
    FreqPoint = factor(names(padded), levels = expected_levels,
                       labels = c("Not at all", "A little", "Some", "A lot")),
    Proportion = as.numeric(padded))} 

df_t3_pc_prop  <- prop_to_df(PQRST_t3_pc_prop,  "pc")
df_t3_fc_prop  <- prop_to_df(PQRST_t3_fc_prop,  "fc")
df_t3_vt_prop  <- prop_to_df(PQRST_t3_vt_prop,  "vt")
df_t3_opr_prop <- prop_to_df(PQRST_t3_opr_prop, "opr")
df_t3_ir_prop  <- prop_to_df(PQRST_t3_ir_prop,  "ir")
df_t3_r_prop   <- prop_to_df(PQRST_t3_r_prop,   "r")
df_t3_sb_prop  <- prop_to_df(PQRST_t3_sb_prop,  "sb")
df_t3_pte_prop <- prop_to_df(PQRST_t3_pte_prop, "pte")


df_t3_prop3 <- bind_rows(
  df_t3_pc_prop,
  df_t3_fc_prop,
  df_t3_vt_prop,
  df_t3_opr_prop,
  df_t3_ir_prop,
  df_t3_r_prop,
  df_t3_sb_prop,
  df_t3_pte_prop)


```

```{r}
#| label: ‘Parent belief data visualisation’
#| echo: false
#| output: true
p1_parent_beliefs <- ggplot(df_t1_prop1, aes(x = Group, y = Proportion, fill = FreqPoint)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Parenting Beliefs",
    y = "Proportion at T1",
    fill = "Response Level",
    title = "T1: within 6 weeks") +
  scale_x_discrete(
    labels = c(
      pc  = "Permanent change",
      fc  = "Family change and damage",
      vt  = "Vulnerability and threat",
      opr = "Other people's reactions",
      ir  = "Inflated responsibility for ensuring safety",
      r   = "Rumination",
      sb  = "Self-blame",
      pte = "Parental tolerance of emotion")) +
  scale_fill_manual(
    values = c(
      "Not at all" = "#d73027",
      "A little"   = "#fc8d59",
      "Some"       = "#fee090",
      "A lot"      = "#91bfdb")) +
  theme_minimal() +
  theme(legend.position = "none",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))

p2_parent_beliefs <- ggplot(df_t2_prop2, aes(x = Group, y = Proportion, fill = FreqPoint)) +
  geom_bar(stat = "identity") +
  labs(
	x = "Parenting Beliefs",
	y = "Proportion at T2",
	fill = "Response Level",
	title = "T2: after 3 months") +
  ylab(NULL) +
  scale_x_discrete(
	labels = c(
  	pc  = "Permanent change",
  	fc  = "Family change and damage",
  	vt  = "Vulnerability and threat",
  	opr = "Other people's reactions",
  	ir  = "Inflated responsibility for ensuring safety",
  	r   = "Rumination",
  	sb  = "Self-blame",
  	pte = "Parental tolerance of emotion")) +
  scale_fill_manual(
	values = c(
  	"Not at all" = "#d73027",
  	"A little"   = "#fc8d59",
      "Some"   	= "#fee090",
  	"A lot"  	= "#91bfdb")) +
  theme_minimal() +
  theme(legend.position = "none",	axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))


p3_parent_beliefs <- ggplot(df_t3_prop3, aes(x = Group, y = Proportion, fill = FreqPoint)) +
  geom_bar(stat = "identity") +
  labs( x = "Parenting Beliefs",
    y = "Proportion at T3",
    fill = "Response Level",
    title = "T3: after 6 months") +
  ylab(NULL) +
  scale_x_discrete(
    labels = c(
      pc  = "Permanent change",
      fc  = "Family change and damage",
      vt  = "Vulnerability and threat",
      opr = "Other people's reactions",
      ir  = "Inflated responsibility for ensuring safety",
      r   = "Rumination",
      sb  = "Self-blame",
      pte = "Parental tolerance of emotion")) +
  scale_fill_manual(
    values = c(
      "Not at all" = "#d73027",
      "A little"   = "#fc8d59",
      "Some"       = "#fee090",
      "A lot"      = "#91bfdb")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))

grid.arrange(p1_parent_beliefs, p2_parent_beliefs, p3_parent_beliefs, ncol = 3)

```

## Design model

```{r}
#| label: ‘create model’
#| echo: false

## create composite scores
dyad_all_clean <- dyad_all_clean %>%
  mutate(
    hot_memory_t1 = rowMeans(select(., contains("actmq_q") & contains("c1_")), na.rm = TRUE),
    cpbq_behaviours_t1 = rowMeans(select(., contains("cpbq") & contains("c1_")), na.rm = TRUE),
    cptci_beliefs_t1 = rowMeans(select(., contains("cptci") & contains("c1_")), na.rm = TRUE),
    pqrst_beliefs_t1 = rowMeans(select(., contains("pqrst_aq") & contains("p1_")), na.rm = TRUE),
    pqrst_behaviours_t1 = rowMeans(select(., contains("pqrst_bq") & contains("p1_")), na.rm = TRUE),
    
    hot_memory_t2 = rowMeans(select(., contains("actmq_q") & contains("c2_")), na.rm = TRUE),
    cpbq_behaviours_t2 = rowMeans(select(., contains("cpbq") & contains("c2_")), na.rm = TRUE),
    cptci_beliefs_t2 = rowMeans(select(., contains("cptci") & contains("c2_")), na.rm = TRUE),
    pqrst_beliefs_t2 = rowMeans(select(., contains("pqrst_aq") & contains("p2_")), na.rm = TRUE),
    pqrst_behaviours_t2 = rowMeans(select(., contains("pqrst_bq") & contains("p2_")), na.rm = TRUE),
    
    hot_memory_t3 = rowMeans(select(., contains("actmq_q") & contains("c3_")), na.rm = TRUE),
    cpbq_behaviours_t3 = rowMeans(select(., contains("cpbq") & contains("c3_")), na.rm = TRUE),
    cptci_beliefs_t3 = rowMeans(select(., contains("cptci") & contains("c3_")), na.rm = TRUE),
    pqrst_beliefs_t3 = rowMeans(select(., contains("pqrst_aq") & contains("p3_")), na.rm = TRUE),
    pqrst_behaviours_t3 = rowMeans(select(., contains("pqrst_bq") & contains("p3_")), na.rm = TRUE))


## specify the model
mod_spec <- '
## Create autoregressive paths
# child hot memory
hot_memory_t2 ~ hot_memory_t1
hot_memory_t3 ~ hot_memory_t2 
# child behaviour
cpbq_behaviours_t2 ~ cpbq_behaviours_t1
cpbq_behaviours_t3 ~ cpbq_behaviours_t2
# child beliefs
cptci_beliefs_t2 ~ cptci_beliefs_t1
cptci_beliefs_t3 ~ cptci_beliefs_t2 
# parent behaviour
pqrst_behaviours_t2 ~ pqrst_behaviours_t1 
pqrst_behaviours_t3 ~ pqrst_behaviours_t2
# parent beliefs
pqrst_beliefs_t2 ~ pqrst_beliefs_t1
pqrst_beliefs_t3 ~ pqrst_beliefs_t2

## Create cross-lagged direct paths
# hot memory loaded on by child beliefs and child behaviour
hot_memory_t2 ~ cpbq_behaviours_t1 + cptci_beliefs_t1
hot_memory_t3 ~ cpbq_behaviours_t2 + cptci_beliefs_t2
# child behaviour loaded on by child beliefs and parent behaviour 
cpbq_behaviours_t2 ~ cptci_beliefs_t1 + pqrst_behaviours_t1
cpbq_behaviours_t3 ~ cptci_beliefs_t2 + pqrst_behaviours_t2
# child beliefs loaded on by parent behaviour and parent beliefs
cptci_beliefs_t2 ~ pqrst_behaviours_t1 + pqrst_beliefs_t1
cptci_beliefs_t3 ~ pqrst_behaviours_t2 + pqrst_beliefs_t2
'

```

Run the model

```{r}
#| label: ‘run model’
# run the model
mod <- lavaan::sem(mod_spec, data = dyad_all_clean, missing = "ML")
# summarise the model
lavaan::summary(mod, fit.measures = TRUE, standardized = TRUE)

```

## Archive

```{r}
#Old code
mod_spec <- '
## hot memory
hot_memory_t1 =~ c1_actmq_q3_t1 + c1_actmq_q5_t1 + c1_actmq_q7_t1 + c1_actmq_q12_t1 + c1_actmq_q15_t1 + c1_actmq_q17_t1

hot_memory_t2 =~ c2_actmq_q3_t2 + c2_actmq_q5_t2 + c2_actmq_q7_t2 + c2_actmq_q12_t2 + c2_actmq_q15_t2 + c2_actmq_q17_t2

hot_memory_t3 =~c3_actmq_q3_t3 + c3_actmq_q5_t3 + c3_actmq_q7_t3 + c3_actmq_q12_t3 + c3_actmq_q15_t3 + c3_actmq_q17_t3


## child behaviour
cpbq_t1 =~c1_cpbq_a_q1_t1 + c1_cpbq_a_q2_t1 + c1_cpbq_a_q3_t1 + c1_cpbq_a_q5_t1 + c1_cpbq_b_q1_t1 + c1_cpbq_b_q2_t1 + c1_cpbq_b_q9_t1 + c1_cpbq_b_q10_t1 + c1_cpbq_b_q11_t1

cpbq_t2 =~ c2_cpbq_a_q1_t2 + c2_cpbq_a_q2_t2 + c2_cpbq_a_q3_t2 + c2_cpbq_a_q5_t2 + c2_cpbq_b_q1_t2 + c2_cpbq_b_q2_t2 + c2_cpbq_b_q9_t2 + c2_cpbq_b_q10_t2 + c2_cpbq_b_q11_t2

cpbq_t3 =~ c3_cpbq_a_q1_t3 + c3_cpbq_a_q2_t3 + c3_cpbq_a_q3_t3 + c3_cpbq_a_q5_t3 + c3_cpbq_b_q1_t3 + c3_cpbq_b_q2_t3 + c3_cpbq_b_q9_t3 + c3_cpbq_b_q10_t3 + c3_cpbq_b_q11_t3



## child beliefs
cptci_t1 =~  c1_cptci_q6_t1 + c1_cptci_q14_t1 + c1_cptci_q19_t1 + c1_cptci_q23_t1 + c1_cptci_q24_t1 + c1_cptci_q1_t1 + c1_cptci_q5_t1 + c1_cptci_q10_t1 + c1_cptci_q18_t1 + c1_cptci_q25_t1

cptci_t2 =~ c2_cptci_q6_t2 + c2_cptci_q14_t2 + c2_cptci_q19_t2 + c2_cptci_q23_t2 + c2_cptci_q24_t2 + c2_cptci_q1_t2 + c2_cptci_q5_t2 + c2_cptci_q10_t2 + c2_cptci_q18_t2 + c2_cptci_q25_t2

cptci_t3 =~ c3_cptci_q6_t3 + c3_cptci_q14_t3 + c3_cptci_q19_t3 + c3_cptci_q23_t3 + c3_cptci_q24_t3 + c3_cptci_q1_t3 + c3_cptci_q5_t3 + c3_cptci_q10_t3 + c3_cptci_q18_t3 + c3_cptci_q25_t3


## Parent behaviours
pqrst_t1 =~ p1_pqrst_bq3_t1 + p1_pqrst_bq4_t1 + p1_pqrst_bq5_t1 + p1_pqrst_bq10_t1 + p1_pqrst_bq11_t1 + p1_pqrst_bq15_t1 + p1_pqrst_bq20_t1 + p1_pqrst_bq22_t1 + p1_pqrst_bq23_t1 + p1_pqrst_bq24_t1 + p1_pqrst_bq26_t1 + p1_pqrst_bq34_t1

pqrst_t2 =~ p2_pqrst_bq3_t2 + p2_pqrst_bq4_t2 + p2_pqrst_bq5_t2 + p2_pqrst_bq10_t2 + p2_pqrst_bq11_t2 + p2_pqrst_bq15_t2 + p2_pqrst_bq20_t2 + p2_pqrst_bq22_t2 + p2_pqrst_bq23_t2 + p2_pqrst_bq24_t2 + p2_pqrst_bq26_t2 + p2_pqrst_bq34_t2

pqrst_t3 =~  p3_pqrst_bq3_t3 + p3_pqrst_bq4_t3 + p3_pqrst_bq5_t3 + p3_pqrst_bq10_t3 + p3_pqrst_bq11_t3 + p3_pqrst_bq15_t3 + p3_pqrst_bq20_t3 + p3_pqrst_bq22_t3 + p3_pqrst_bq23_t3 + p3_pqrst_bq24_t3 + p3_pqrst_bq26_t3 + p3_pqrst_bq34_t3


## Parent beliefs
pqrst_beliefs_t1 =~ p1_pqrst_aq2_t1 + p1_pqrst_aq4_t1   + p1_pqrst_aq6_t1 + p1_pqrst_aq9_t1
      + p1_pqrst_aq14_t1 + p1_pqrst_aq17_t1 + 
      p1_pqrst_aq22_t1 + 
      p1_pqrst_aq26_t1 + p1_pqrst_aq27_t1 + p1_pqrst_aq29_t1 + p1_pqrst_aq31_t1 + p1_pqrst_aq33_t1 + 
      p1_pqrst_aq34_t1 + p1_pqrst_aq35_t1 + p1_pqrst_aq36_t1 + p1_pqrst_aq37_t1 + p1_pqrst_aq41_t1 + 
      p1_pqrst_aq42_t1

pqrst_beliefs_t2 =~ p2_pqrst_aq2_t2 + p2_pqrst_aq4_t2 + p2_pqrst_aq6_t2 + p2_pqrst_aq9_t2 + p2_pqrst_aq14_t2 + p2_pqrst_aq17_t2 + p2_pqrst_aq22_t2 + p2_pqrst_aq26_t2 + p2_pqrst_aq27_t2 + p2_pqrst_aq29_t2 + p2_pqrst_aq31_t2 + p2_pqrst_aq33_t2 + p2_pqrst_aq34_t2 + p2_pqrst_aq35_t2 + p2_pqrst_aq36_t2 + p2_pqrst_aq37_t2 + p2_pqrst_aq41_t2 + p2_pqrst_aq42_t2


      
pqrst_beliefs_t3 =~ p3_pqrst_aq2_t3 + p3_pqrst_aq4_t3 + p3_pqrst_aq6_t3 + p3_pqrst_aq9_t3 + p3_pqrst_aq14_t3 + p3_pqrst_aq17_t3 + p3_pqrst_aq22_t3 + p3_pqrst_aq26_t3 + p3_pqrst_aq27_t3 + p3_pqrst_aq29_t3 + p3_pqrst_aq31_t3 + p3_pqrst_aq33_t3 + p3_pqrst_aq34_t3 + p3_pqrst_aq35_t3 + p3_pqrst_aq36_t3 + p3_pqrst_aq37_t3 + p3_pqrst_aq41_t3 + p3_pqrst_aq42_t3


## Create autoregressive paths
# child hot memory
hot_memory_t2 ~ hot_memory_t1
hot_memory_t3 ~ hot_memory_t2 
# child behaviour
cpbq_t2 ~ cpbq_t1
cpbq_t3 ~ cpbq_t2
# child beliefs
cptci_t2 ~ cptci_t1
cptci_t3 ~ cptci_t2 
# parent behaviour
pqrst_t2 ~ pqrst_t1 
pqrst_t3 ~ pqrst_t2
# parent beliefs
pqrst_beliefs_t2 ~ pqrst_beliefs_t1
pqrst_beliefs_t3 ~ pqrst_beliefs_t2

## Create cross-lagged direct paths
# hot memory loaded on by child beliefs and child behaviour
hot_memory_t2 ~ cpbq_t1 + cptci_t1
hot_memory_t3 ~ cpbq_t2 + cptci_t2
# child behaviour loaded on by child beliefs and parent behaviour 
cpbq_t2 ~ cptci_t1 + pqrst_t1
cpbq_t3 ~ cptci_t2 + pqrst_t2
# child beliefs loaded on by parent behaviour and parent beliefs
cptci_t2 ~ pqrst_t1 + pqrst_t1
cptci_t3 ~ pqrst_t2 + pqrst_t2
'
# Merge them into a single dyadic dataset
# dyad_all <- full_join(child_all, parent_all, by = "dyad_ID", suffix = c("_child", "_parent"))

# Merge them into a single dyadic dataset
# dyad_all <- full_join(child_all, parent_all, by = "dyad_ID", suffix = c("_child", "_parent"))


## Combine parent and child datasets long
## Add group variable
# parent_all <- parent_all |>
#  mutate(group = "parent")
# child_all <- child_all |>
#  mutate(group = "child")

# Rename ID so they are not duplicate
# parent_all <- parent_all |>
#  mutate(ID = paste0("P_", ID), group = "parent")
# child_all <- child_all |>
#  mutate(ID = paste0("C_", ID), group = "child")

## Combine both datasets, wide
# combined_all <- bind_rows(parent_all, child_all)

```
